---
title: "Definitions of the MINE Statistics"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Definitions of the MINE Statistics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(tidymine)
```

`tidymine` calculates several statistics. This page is to guide you through them.

## TL;DR

Statistic | Interpretation | Answers the question
--- | --- | ---
MIC | Information content | "How useful is $x$ to know $y$?"
MAS | Non-monotonicity | "How much does the function go up and down?"
MEV | Function-ness | "How close is this to being a continuous function?"
MCN | Complexity | "How much do the values move around?"

Reference: 10.1126/science.1205438

## Maximal Information Coefficient (MIC)

MIC is the main statistic, calculating how much information variable $x$ has about $y$. You can use it as a more sophisticated correlation. It is able to pick up on many more relations than correlation.


## Maximum Asymmetry Score (MAS)

This is a measure of *non-monotonicity*. This is roughly 'how much the function goes up and down'.

## 
